
\documentclass[a4paper,12pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{eurosym}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}

 
\renewcommand*\refname{Kaynaklar}
\def\ms{\textsc{2010 AMS S\.{i}n\.{i}fland\.{i}rmas\.{i}: }}
\providecommand\key[1]{\par \textsc{Anahtar Kelimeler :}#1 \vspace{0,5cm}}
\providecommand\add[2]{\emph{{#1}} {\newline  E-Posta : \emph{#2}}}
\textheight 23cm \textwidth 13.0cm
 \oddsidemargin=1.4cm
  \evensidemargin=1.4cm
\topmargin=-0.4cm
 
\begin{document}

\title{Primitive cohomology of smooth projective complete and non-complete intersections}
\author{Javier Fernandez de Bobadilla}
\date{}
\maketitle

\begin{center}
{\Large Abstract}
\end{center}

Work in progress. 

Let $X$ be a smooth projective manifold. Let $F_1,...,F_r$ be a set of homogeneous polynomials, all of them of the same degree (sufficiently high) defining $X$ as a 
subscheme of the projective space. Let $c$ be the codimension of $X$. Pick $G_1,...,G_c$, $c$ generic linear combinations of $F_1,...,F_r$. The complete intersection 
$Z_0:=V(G_1,...,G_c)$ contains $X$ as an irreducible component. Let 
$$Z_t:=V(G_{1,t},...,G_{c,t})$$
be a $1$-parameter smoothing of $Z_0$. Our aim is to compare the 
intermediate primitive cohomology of $X$ (for a certain polarisation) with the intermediate cohomology of $Z_t$.

If $\dim(X)\leq 3$ we find a natural embedding of the intermediate primitive cohomology of $X$ into the intermediate cohomology of $Z_t$. For $\dim(X)\geq 4$ this embedding does
not exist in general. We find a necessary and sufficient condition: we define two polynomials $P$ and $Q$ on the Chern classes of the tangent bundle of $X$ and 
on the polarisation given by the embedding, and the cohomology embedding holds if and only if $Q$ is a multiple of $P$ in the cohomology ring of $X$. 

The condition is satisfied inmediately if $X$ is a complete intersection, but also if the codimension of $X$ is sufficiently low. This may be seen as a supporting evidence of 
Hartshorne conjecture on smooth varieties of small codimension being complete intersections, and perhaps as a tool to address it.

In the case that the condition is not satisfied, the piece of the primitive cohomology that does not embed is shown to embed into the intermediate primitive cohomology of a manifold of dimension 4 less that the original one, setting up in this way an inductive scheme to analyze it.

\end{document}
